SSwAB-IT Phase 1 Analysis

### 2024-12-18 Jordana Hoppe/SSwAB-IT/phase_1_analysis.qmd
new age groups SSwAB-IT

---
title: "SSwAB-IT Phase 1 Analysis"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
editor: source
---

@@

@@

db_demographics$age_at_cos <- as.numeric(difftime(db_demographics$cos_collection_date,

@@

@@

  c(-Inf, 10, 18, 30, Inf),

@@

    record_id,

@@

@@

```{r}
db_demographics %>%
  select(group, age_at_cos, age_group, sex, Race, Ethnicity) %>%
  tbl_summary(
    by = group, missing_text = "Missing",
    statistic = all_continuous() ~ c("{median} ({min}, {max})"),
    label = list(
      "sex" = "Sex", "age_at_cos" = "Age at COS", "age_group" = "Age Group"
    )
  ) %>%
  add_overall() %>%
  add_p(test = list(c("Race", "Ethnicity") ~ "fisher.test")) %>%
  separate_p_footnotes() %>%
  as_gt()
```

@@

```{r}
agreement <- function(bug, data = df) {
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos)]
  colnames(d) <- c("COS", "SOS")
  d <- d[complete.cases(d), ]
  # Agreement metrics
  c <- confusionMatrix(d$SOS,
    reference = d$COS,
    positive = "Positive", mode = "everything",
    dnn = c("SOS", "COS")
  )
  # Print
  cat("\n")
  cat("####", "2x2 Table")
  cat("\n")
  d %>%
    tbl_cross(percent = "cell") %>%
    print()
  cat("\n")
  cat("####", "2x2 Table (With CIs)")
  cat("\n")
  d %>%
    tbl_summary(by = COS, percent = "cell") %>%
    add_ci(method = list(all_categorical() ~ "wald")) %>%
    print()
  cat("\n")
  cat("Overall accuracy (both negative/negative and positive/positive) was ",
    scales::percent(c$overall["Accuracy"], accuracy = 0.1), " (95% CI: ",
    scales::percent(c$overall["AccuracyLower"], accuracy = 0.1), " - ",
    scales::percent(c$overall["AccuracyUpper"], accuracy = 0.1), ").",
    sep = ""
  )
  cat("\n")
  cat("\n")
  cat("Kappa was ", round(c$overall["Kappa"], 3), ".", sep = "")
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of negative results")
  cat("\n")
  print(plot(euler(d == "Negative"),
    quantities = list(cex = 3),
    fills = list(fill = c("#FFC107", "#1E88E5", "#004D40"))
  ))
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of positive results")
  cat("\n")
  print(plot(euler(d == "Positive"),
    quantities = list(cex = 3),
    fills = list(fill = c("#FFC107", "#1E88E5", "#004D40"))
  ))
  cat("\n")
}
agreement_test <- function(bug, group = "group", data = df) {
  # Prepare data
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos, group)]
  d <- d[complete.cases(d), ]
  colnames(d) <- c("COS", "SOS", "Group")
  # Agreement and detailed agreement
  d$agree <- d$COS == d$SOS
  d$detailed_agree <- paste0("COS ", d$COS, "/", "SOS ", d$SOS)
  # Print
  cat("\n")
  d %>%
    select(agree, detailed_agree, Group) %>%
    tbl_summary(by = Group, missing_text = "Missing", label = list(
      agree ~ "Agree (Both Positive/Positive and Negative/Negative)",
      detailed_agree ~ "Detailed Agreement"
    )) %>%
    add_overall() %>%
    add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e6)) %>%
    separate_p_footnotes() %>%
    print()
  cat("\n")
}
```

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  print(b)
  cat("\n")
  cat("##", as.character(bug_list[b]))
  cat("\n")
  cat("###", "Overall agreement")
  cat("\n")
  agreement(b)
  cat("\n")
  cat("###", "Agreement by group")
  cat("\n")
  agreement_test(b)
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("####", "Agreement by age group")
  cat("\n")
  agreement_test(b, group = "age_group")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("####", "Agreement by gender assigned at birth")
  cat("\n")
  agreement_test(b, group = "age_group")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("####", "Agreement by Azithromycin status")
  cat("\n")
  agreement_test(b, group = "azithromycin")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("####", "Agreement by inhaled Tobramycin status")
  cat("\n")
  agreement_test(b, group = "inhaled_tobramycin")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("####", "Agreement by inhaled Aztreonam status")
  cat("\n")
  agreement_test(b, group = "inhaled_aztreonam")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("####", "Agreement by inhaled Colisitin status")
  cat("\n")
  agreement_test(b, group = "inhaled_colisitin")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("####", "Agreement by inhaled Vancomycin status")
  cat("\n")
  agreement_test(b, group = "inhaled_vancomycin")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("####", "Agreement by other inhaled antibiotics status")
  cat("\n")
  agreement_test(b, group = "other_inhaled_antibiotics")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("####", "Agreement by chronic oral antibiotic status")
  cat("\n")
  agreement_test(b, group = "chronic_oral_antibiotic")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("####", "Agreement by CFTR modulator status")
  cat("\n")
  agreement_test(b, group = "cftr_modulator")
  cat("\n")
}))
```

>>>>

---
title: "SSwAB-IT Phase 1 Analysis"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 10
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
editor: source
---

@@

df <- full_join(df,
  db_selfobtained_sample[, c("record_id", "who_collected_the_sos")],

@@

db_demographics$age_at_cos <-
  as.numeric(difftime(db_demographics$cos_collection_date,

@@

# 1-5, 6-11, 12-17 and 18+ years

@@

  c(-Inf, 6, 12, 18, Inf),

@@

    record_id, who_collected_cos, who_collected_the_sos,

@@

# Drop unused levels
df$who_collected_cos <- droplevels(df$who_collected_cos)

@@

```{r}
db_demographics %>%
  select(group, age_at_cos, age_group, sex, Race, Ethnicity) %>%
  tbl_summary(
    by = group, missing_text = "Missing",
    statistic = all_continuous() ~ c("{median} ({min}, {max})"),
    label = list(
      "sex" = "Sex", "age_at_cos" = "Age at COS", "age_group" = "Age Group"
    )
  ) %>%
  add_overall() %>%
  add_p(
    test = list(c("Race", "Ethnicity") ~ "fisher.test"),
    test.args = age_group ~ list(workspace = 2e9)
  ) %>%
  separate_p_footnotes() %>%
  as_gt()
```

@@

```{r}
agreement <- function(bug, data = df) {
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos)]
  colnames(d) <- c("COS", "SOS")
  d <- d[complete.cases(d), ]
  # Agreement metrics
  c <- confusionMatrix(d$SOS,
    reference = d$COS,
    positive = "Positive", mode = "everything",
    dnn = c("SOS", "COS")
  )
  # Print
  cat("\n")
  cat("\n")
  cat("####", "2x2 Table")
  cat("\n")
  cat("\n")
  d %>%
    tbl_cross(percent = "cell") %>%
    print()
  cat("\n")
  cat("\n")
  cat("####", "2x2 Table (With CIs)")
  cat("\n")
  cat("\n")
  d %>%
    tbl_summary(by = COS, percent = "cell") %>%
    add_ci(method = list(all_categorical() ~ "wald")) %>%
    print()
  cat("\n")
  cat("\n")
  cat("Overall accuracy (both negative/negative and positive/positive) was ",
    scales::percent(c$overall["Accuracy"], accuracy = 0.1), " (95% CI: ",
    scales::percent(c$overall["AccuracyLower"], accuracy = 0.1), " - ",
    scales::percent(c$overall["AccuracyUpper"], accuracy = 0.1), ").",
    sep = ""
  )
  cat("\n")
  cat("\n")
  cat("Kappa was ", round(c$overall["Kappa"], 3), ".", sep = "")
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of negative results")
  cat("\n")
  cat("\n")
  print(plot(euler(d == "Negative"),
    quantities = list(cex = 3),
    fills = list(fill = c("#FFC107", "#1E88E5", "#004D40"))
  ))
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of positive results")
  cat("\n")
  cat("\n")
  print(plot(euler(d == "Positive"),
    quantities = list(cex = 3),
    fills = list(fill = c("#FFC107", "#1E88E5", "#004D40"))
  ))
  cat("\n")
  cat("\n")
}
agreement_test <- function(bug, group = "group", data = df) {
  # Prepare data
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos, group)]
  d <- d[complete.cases(d), ]
  colnames(d) <- c("COS", "SOS", "Group")
  # Agreement and detailed agreement
  d$agree <- d$COS == d$SOS
  d$detailed_agree <- paste0("COS ", d$COS, "/", "SOS ", d$SOS)
  # Print
  cat("\n")
  cat("\n")
  d %>%
    select(agree, detailed_agree, Group) %>%
    tbl_summary(by = Group, missing_text = "Missing", label = list(
      agree ~ "Agree (Both Positive/Positive and Negative/Negative)",
      detailed_agree ~ "Detailed Agreement"
    )) %>%
    add_overall() %>%
    add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e9)) %>%
    separate_p_footnotes() %>%
    print()
  cat("\n")
  cat("\n")
}
```

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  print(b)
  cat("\n")
  cat("\n")
  cat("##", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("###", "Overall agreement")
  cat("\n")
  cat("\n")
  agreement(b)
  cat("\n")
  cat("\n")
  cat("###", "Agreement by group")
  cat("\n")
  cat("\n")
  agreement_test(b)
  cat("\n")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by age group")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "age_group")
  cat("\n")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by gender assigned at birth")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "age_group")
  cat("\n")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by Azithromycin status")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "azithromycin")
  cat("\n")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by inhaled Tobramycin status")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "inhaled_tobramycin")
  cat("\n")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by inhaled Aztreonam status")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "inhaled_aztreonam")
  cat("\n")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by inhaled Colisitin status")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "inhaled_colisitin")
  cat("\n")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by inhaled Vancomycin status")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "inhaled_vancomycin")
  cat("\n")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by other inhaled antibiotics status")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "other_inhaled_antibiotics")
  cat("\n")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by chronic oral antibiotic status")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "chronic_oral_antibiotic")
  cat("\n")
  cat("\n")
}))
```

@@

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by CFTR modulator status")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "cftr_modulator")
  cat("\n")
  cat("\n")
}))
```

## Who collected the COS

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by who collected the COS")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "who_collected_cos")
  cat("\n")
  cat("\n")
}))
```

## Who collected the SOS

```{r results='asis'}
#| message: false
invisible(lapply(names(bug_list), function(b) {
  cat("\n")
  cat("\n")
  cat("###", as.character(bug_list[b]))
  cat("\n")
  cat("\n")
  cat("####", "Agreement by who collected the SOS")
  cat("\n")
  cat("\n")
  agreement_test(b, group = "who_collected_the_sos")
  cat("\n")
  cat("\n")
}))
```
